---
title: "R Notebook"
output: html_notebook
---

```{r}

library(tidyverse)
library(haven)
library(stringr)

```

Instructions to obtain EVS/WVS 1981-2022 trend file (Integrated Values Survey - IVS):

1. Go to https://www.worldvaluessurvey.org/WVSEVStrend.jsp

2. Download the following data-sets and syntax file:
  * EVS Trend File 1981-2017 (ZA7503_v3-0-0.dta.zip Stata)
  * WVS Trend File 1981-2022 (3.0.0) (WVS_Trend_1981_2022_v3.0 Stata)
  * EVS_WVS_MergeSyntax_Stata.zip
  
3. Run IVS merge syntax in Stata and save dta file as "../data-raw/Integrated_values_surveys_1981-2021.dta".

! Obs.: The newest IVS data does not contain a 'sample' variable differentiating West from East Germany. We therefore used the 'sample' variable of the previous version of the IVS (EVS/WVS 1981-2014 trend file) for that purpose. From this older trend file, we used only German data concerning the five following variables: 
  - Original respondent id (S006)
  - Year (S020)
  - Sample (S003A)
  - Region (X048)*
* Since the 'sample' variable in WVS wave 3 (1997) does not differentiate West from East Germany, for this wave we used 'Region' to separate the samples.
  - Weight (S017A)
The clean data-set is on this project's Github under the name 'Germany-sample-data.rds'. The chunk 'Clean data' below uses 'Original respondent id' and 'Year' to join the newest IVS data with the Germany sample data. 

# Read data:
```{r}

wvsevs_full <- read_dta("../data-raw/Integrated_values_surveys_1981-2021.dta")

germany_sample_data <- read_csv("../data-raw/Germany-sample-data.csv")

```

# Clean data:
```{r}

# Select relevant variables:
wvsevs_clean <- wvsevs_full %>% 
  select(source = S001,
         wave_wvs = S002,
         wave_evs = S002EVS,
         country = S003,
         resp_id = S007,
         original_id = S006,
         sex = X001,
         age = X003,
         weight = S017,
         year = S020,
         instructions_work = C061,
         just_abortion = F120,
         just_adultery = F128,
         just_divorce = F121,
         just_euthanasia = F122,
         just_homosexuality = F118,
         just_killing_selfdefence = F144,
         just_lying = F127,
         just_money_found = F140,
         just_parents_children = F114C,
         just_prostitution = F119,
         just_sex_before_marriage = F135A,
         just_soft_drugs = F126,
         just_suicide = F123,
         respect_love_parents = A025,
         parents_responsibilities = A026,
         sexual_freedom = D024,
         woman_single_parent = D023)
         
wvsevs_clean <- wvsevs_clean %>%
  mutate_at(vars(source, matches("wave"), country, sex), ~as_factor(.)) %>% 
  mutate_at(vars(matches("wave"), country, sex), ~as.character(.)) %>% 
  # Re-code missing values:
  mutate_at(vars(instructions_work:woman_single_parent), ~ifelse(str_detect(., "NA"), NA_character_, .)) %>%
  # Coalesce wave variables:
  mutate(wave = coalesce(wave_wvs, wave_evs)) %>% 
  select(source, wave, country, resp_id:woman_single_parent)

# Clean country names and create sample variable:
wvsevs_clean <- wvsevs_clean %>% 
  mutate(country = case_when(
            country == "Czechia" ~ "Czech Republic",
            country == "Taiwan ROC" ~ "Taiwan",
            country == "Dominican Rep." ~ "Dominican Republic",
            TRUE ~ country)) %>% 
  # Add Germany East/West split data:
  left_join(germany_sample_data) %>% 
  mutate(sample = ifelse(country == "Germany", sample, country),
         weight = ifelse(country == "Germany", sample_weight, weight)) %>% 
  # Drop Germany's last wave, given that it is not possible to distinguish between East and West Germany then:
  drop_na(sample) %>% 
  select(source:country, sample, year, resp_id, sex:woman_single_parent) %>% 
  zap_labels()

```

# Re-code answers to 0/1:

CODEBOOK:

instructions_work: "Follow instructions" (1); "Must be convinced first", "Depends" (0)

parents_responsibilities: "Parents´ duty is to do their best for their children even at" (1); "Parents have a life of their own and should not be asked to", "Neither" (0)

respect_love_parents: "Always respect" (1); "Respect if earned", "Neither" (0)

woman_single_parent: "Approve" (1); "Disapprove", "Depends" (0)

sexual_freedom: "Agree" (1); "Disagree", "Neither"

justifiables: "Always justifiable", 6-9 (1); "Never justifiable", 2:5 (0)

```{r}

wvsevs_data_recoded <- wvsevs_clean %>% 
  mutate_at(vars(instructions_work, parents_responsibilities, respect_love_parents, woman_single_parent, sexual_freedom), ~ifelse(. == 1, 1, 0)) %>% 
  mutate_at(vars(matches("just")), ~case_when(. %in% c(6:10) ~ 1, 
                                              . %in% c(1:5) ~ 0,
                                              . %in% c(-5:-1) ~ NA_real_))
         
# Reshape data to long format:
wvsevs_data_long <- wvsevs_data_recoded %>%
    select(-wave) %>%
    pivot_longer(c(-source:-weight),
                 names_to = "issue", 
                 values_to = "opinion") %>%
    drop_na(opinion)

write_rds(wvsevs_data_long, "../data-processed/WVS-EVS_time-series-data_1981-2014_long.rds")

```







