---
title: "R Notebook"
output: html_notebook
---

```{r}

library(tidyverse)
library(haven)

```

# Read data:
```{r}

# Argument advantage data - U.S. and Greece - long format:
aa_data_long <- read_csv("../data-raw/argument-advantage-data_US & Greece_feb-2023_long.csv")

```

# Exclude participants who scored less than 6 on wordsum:
```{r}

# Participants to exclude from U.S. sample:
toexclude_us <- aa_data_long %>% 
  filter(country == "United States of America") %>% 
  select(id, matches("ws")) %>% 
  unique() %>% 
  pivot_longer(cols = c(matches("ws")),
               names_to = "var",
               values_to = "value") %>%
  mutate(correct = case_when(
    var == "ws1" & value == 4 ~ 1,
    var == "ws2" & value == 2 ~ 1,
    var == "ws3" & value == 5 ~ 1,
    var == "ws4" & value == 5 ~ 1,
    var == "ws5" & value == 1 ~ 1,
    var == "ws6" & value == 4 ~ 1,
    var == "ws7" & value == 3 ~ 1,
    var == "ws8" & value == 1 ~ 1,
    var == "ws9" & value == 5 ~ 1,
    var == "ws10" & value == 1 ~ 1,
    TRUE ~ 0)) %>% 
  group_by(id) %>% 
  summarise(sum(correct)) %>% 
  filter(`sum(correct)` < 6) %>% 
  pull(id)

# Participants to exclude from Greek sample:
toexclude_greece <- aa_data_long %>% 
  filter(country == "Greece") %>%  
  select(id, matches("ws")) %>% 
  unique() %>% 
  pivot_longer(cols = c(matches("ws")),
               names_to = "var",
               values_to = "value") %>% 
  group_by(id) %>% 
  summarise(sum(value)) %>% 
  filter(`sum(value)` < 6) %>% 
  pull(id)

# 15 participants in total were excluded.
aa_data_long <- aa_data_long %>% 
  filter(!id %in% toexclude_us & !id %in% toexclude_greece)
  
```

# Calculate pro-positions' argument advantage:
```{r}

# Create a 'moral foundation' variable:
aa_data_long <- aa_data_long %>% 
  mutate(argument = as.character(argument),
         mf = fct_collapse(argument,
                           harm = c("1", "2", "3"),
                           fair = c("4", "5", "6"),
                           ingr = c("7", "8", "9"),
                           auth = c("10", "11", "12"),
                           puri = c("13", "14", "15"),
                           libe = c("16", "17", "18"),
                           viol = c("19", "20", "21")))

# Re-scale applicability ratings so that values range between 0 and 1:
range01 <- function(x, ...){
  (x - min(x, ...)) / (max(x, ...) - min(x, ...))
  }

aa_data_long <- aa_data_long %>% 
  mutate(value_sc = range01(value, na.rm = TRUE))

write_rds(aa_data_long, "../data-processed/argument-advantage-data_US & Greece_long_clean.rds")

# Calculate moral foundations' average applicability:
mf_app <- aa_data_long %>% 
  group_by(source, issue, position, mf, argument) %>% 
  summarise(value_sc = mean(value_sc, na.rm = TRUE)) %>% 
  group_by(source, issue, position, mf) %>% 
  summarise(value_sc = mean(value_sc))  

# Calculate pro-positions' argument advantage:
mf_adv <- mf_app %>% 
  spread(position, value_sc) %>% 
  mutate(arg_adv = yes - no) %>% 
  select(-no, -yes) %>% 
  spread(mf, arg_adv) %>% 
  mutate(hflv = (harm + fair + libe + viol)/4) %>% 
  # Reverse hlfv measure of 'premars1':
  mutate(hflv = ifelse(issue == "premars1", hflv*-1, hflv))

```

# Descriptive statistics:
```{r}

# Sample sizes:
sample_sizes <- aa_data_long %>% 
  distinct(id, country) %>% 
  group_by(country) %>% 
  summarise(n_respondents = n_distinct(id)) %>% 
  bind_rows(aa_data_long %>% 
              summarise(n_respondents = n_distinct(id)) %>% 
              mutate(country = "Combined")) %>% 
  rename(`Country:` = country,
         `Number of respondents:` = n_respondents)

# Number of exclusions based on English proficiency:
excluded <- tibble(
  `Country:` = "United States of America",
  `Excluded:` = length(toexclude_us)) %>% 
  bind_rows(tibble(
  `Country:` = "Greece",
  `Excluded:` = length(toexclude_greece))) %>% 
  bind_rows(tibble(
  `Country:` = "Combined",
  `Excluded:` = length(toexclude_us) + length(toexclude_greece)))

# Gender:
gender_stats <- aa_data_long %>% 
  distinct(id, country, gender) %>% 
  group_by(country, gender) %>% 
  summarise(n_respondents = n_distinct(id)) %>% 
  spread(gender, n_respondents) %>% 
  bind_rows(aa_data_long %>%
              distinct(id, country, gender) %>% 
              group_by(gender) %>% 
              summarise(n_respondents = n_distinct(id)) %>% 
              spread(gender, n_respondents) %>% 
              mutate(country = "Combined")) %>% 
  rename(`Country:` = country)

# Age:
age_stats <- aa_data_long %>% 
  distinct(id, country, age) %>% 
  group_by(country) %>% 
  summarise(`Mean age:` = round(mean(age), 2),
            `SD age:` = round(sd(age), 2)) %>% 
  bind_rows(aa_data_long %>%
              distinct(id, age) %>% 
              summarise(`Mean age:` = round(mean(age), 2),
                        `SD age:` = round(sd(age), 2)) %>% 
              mutate(country = "Combined")) %>% 
  rename(`Country:` = country)

(descriptive_stats <- sample_sizes %>% 
  left_join(excluded) %>% 
  left_join(gender_stats) %>% 
  left_join(age_stats) %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_classic())
  
```

Number of times items were judged (combined for U.S. and Greek samples):
```{r}

aa_data_long %>% 
  distinct(id, issue, answer) %>% 
  group_by(issue) %>% 
  count() %>% 
  ungroup() %>% 
  summarise(`Number of times items were judged, on average:` = mean(n),
            `Item judged the least:` = min(n)) %>% 
  kableExtra::kbl()
  
```

# Extra: data collection for hypothesis 2 - robustness check:
```{r}

extra_hflv_long <- read_csv("../data-raw/argument-advantage-data_additional-issues_jun-2023_long.csv")

```

Exclude participants who scored less than 6 on wordsum:
```{r}

# Participants to exclude:
toexclude <- extra_hflv_long %>% 
  select(id, matches("ws")) %>% 
  unique() %>% 
  pivot_longer(cols = c(matches("ws")),
               names_to = "var",
               values_to = "value") %>%
  group_by(id) %>% 
  summarise(sum(value)) %>% 
  filter(`sum(value)` < 6) %>% 
  pull(id)

# 5 participants were excluded.
extra_hflv_long <- extra_hflv_long %>% 
  filter(!id %in% toexclude)

```

Calculate pro-positions' argument advantage:
```{r}

# Create a 'moral foundation' variable:
extra_hflv_long <- extra_hflv_long %>% 
  mutate(argument = as.character(argument),
         mf = fct_collapse(argument,
                           harm = c("1", "2", "3"),
                           fair = c("4", "5", "6"),
                           ingr = c("7", "8", "9"),
                           auth = c("10", "11", "12"),
                           puri = c("13", "14", "15"),
                           libe = c("16", "17", "18"),
                           viol = c("19", "20", "21")))

# Re-scale applicability ratings so that values range between 0 and 1:
range01 <- function(x, ...){
  (x - min(x, ...)) / (max(x, ...) - min(x, ...))
  }

extra_hflv_long <- extra_hflv_long %>% 
  mutate(value_sc = range01(value, na.rm = TRUE))

# Calculate moral foundations' average applicability:
extra_mf_app <- extra_hflv_long %>% 
  group_by(issue, position, mf, argument) %>% 
  summarise(value_sc = mean(value_sc, na.rm = TRUE)) %>% 
  group_by(issue, position, mf) %>% 
  summarise(value_sc = mean(value_sc))  

# Calculate pro-positions' argument advantage:
extra_mf_adv <- extra_mf_app %>% 
  spread(position, value_sc) %>% 
  mutate(arg_adv = yes - no) %>% 
  select(-no, -yes) %>% 
  spread(mf, arg_adv) %>% 
  mutate(hflv = (harm + fair + libe + viol)/4)

# Add 'just_sex_before_marriage', whose hflv is the inverse of that of the ISSP issue 'premars1':
extra_mf_adv <- extra_mf_adv %>% 
  bind_rows(mf_adv %>% 
              filter(issue == "premars1") %>% 
              mutate_at(vars(harm:hflv), ~.*-1) %>% 
              mutate(issue = "just_sex_before_marriage")) %>% 
  mutate(source = "WVS/EVS")

```

Demographics:
```{r}

# Number of moral items:
extra_hflv_long %>% 
  distinct(issue) %>% 
  count()
# Obs.: For the WVS issue 'just_sex_before_marriage' we simply used the reversed aa of the ISSP issue 'premars1'. Thus, there are 8 new issues in the complementary analysis. 

# How many times each item was rated?
extra_hflv_long %>% 
  group_by(issue) %>% 
  summarise(n_resp = n_distinct(id)) %>% 
  summarise(min(n_resp),
            mean(n_resp))

# Number of respondents:
extra_hflv_long %>% 
  distinct(id) %>% 
  count()

# Average age:
extra_hflv_long %>% 
  distinct(id, age) %>% 
  summarise(mean(age),
            sd(age))

# Proportion of women:
extra_hflv_long %>%
  distinct(id, gender) %>% 
  mutate(gender_01 = gender - 1) %>% 
  summarise(mean(gender_01))
  
```

# Combine argument advantage data-sets:
```{r}

mf_adv <- mf_adv %>% 
  bind_rows(extra_mf_adv)

write_rds(mf_adv, "../data-processed/argument-advantage-data_US & Greece_clean.rds")

```



