---
title: "R Notebook"
output: html_notebook
---


```{r}

library(tidyverse)
library(lme4)
library(boot)
library(ggrepel)

```

# Read data:
```{r}

# Aggregated time-series data plus argument advantage data:
issp_common_issues <- read_rds("../data-processed/ISSP_15-issues-measured-in-the-same-14-countries.rds")
wvsevs_common_issues <- read_rds("../data-processed/WVS_10-issues-measured-in-the-same-50-countries.rds")

```

# Time trends:

Time trends functions:
```{r}

estimate_logit_cntry <- function(data) {
 m <- glm(cbind(n_agree, n_disagree) ~ year_r + sample,
          data, 
          family = quasibinomial(link = "logit"))
 coef(m)["year_r"]
}

estimate_logit <- function(data) {
 m <- glm(cbind(n_agree, n_disagree) ~ year_r,
          data, 
          family = quasibinomial(link = "logit"))
 coef(m)["year_r"]
}

```

Calculate time trends, by issue:
```{r}

# ISSP:
issp_common_issues_byissue <- issp_common_issues %>%
  group_nest(issue, label, hflv) 

issp_trends <- issp_common_issues_byissue %>%
  mutate(logit_est = map_dbl(data, estimate_logit_cntry)) 


# WVS/EVS:
wvsevs_common_issues_byissue <- wvsevs_common_issues %>%
  group_nest(issue, label, hflv) 

wvsevs_trends <- wvsevs_common_issues_byissue %>%
  mutate(logit_est = map_dbl(data, estimate_logit_cntry)) 

```

# Results:

## Table 1:
```{r}

issp_trends %>% 
  select(-data) %>% 
  mutate(source = "ISSP") %>% 
  bind_rows(wvsevs_trends %>% 
              select(-data) %>% 
              mutate(source = "WVS")) %>% 
  mutate_at(vars(hflv, logit_est), ~round(., 2)) %>%
  select(Source = source, Opinion = label, `Global change rate` = logit_est, `Arg. adv.` = hflv) %>%
  arrange(Source, desc(`Arg. adv.`)) %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_classic(full_width = FALSE)
  
```

## Hypothesis 1: Moral Argument Realism. 

Read data:
```{r}

# Argument advantage data - long format:
aa_long <- read_rds("../data-processed/argument-advantage-data_US & Greece_long_clean.rds") %>% 
  select(id, country, age, gender, source, issue, answer, position:argument, mf, value, value_sc) 

# Create age groups:
median_age <- aa_long %>% 
  distinct(country, id, age) %>% 
  summarise(median(age)) %>% 
  pull(`median(age)`)

aa_long <- aa_long %>%
  mutate(age = as.numeric(age),
         age_group = ifelse(age > median_age, "Older", "Younger")) 
  
```

Calculate pro-positions' argument advantage in each subsample:
```{r}

# Function to get susamples' argument advantage:
get_subsamples_aa <- function(data, group) {

# Calculate moral foundations' average applicability per issue position:
mf_app <- data %>% 
  group_by({{group}}, source, issue, position, mf) %>% 
  summarise(value_sc = mean(value_sc, na.rm = TRUE))  

# Calculate pro-positions' argument advantage:
mf_adv <- mf_app %>% 
  spread(position, value_sc) %>% 
  mutate(arg_adv = yes - no) %>% 
  select(-no, -yes) %>% 
  spread(mf, arg_adv) %>% 
  mutate(hflv_pro = (harm + fair + libe + viol)/4)

mf_adv <- mf_adv %>% 
  select({{group}}, source, issue, hflv_pro) %>% 
  spread({{group}}, hflv_pro) %>% 
  rename(Source = source)

# Return:
mf_adv

}


# United states vs. Greece:
mf_adv_bycountry <- get_subsamples_aa(aa_long, country)

# Males vs. Females:
mf_adv_bygender <- get_subsamples_aa(aa_long, gender) %>% 
  select(-Other)

# Younger vs. Older:
mf_adv_byage <- get_subsamples_aa(aa_long, age_group)

```

Get observed concordance correlation coefficients (CCCs):
```{r}

# US vs. Greece:
ccc_country <- DescTools::CCC(mf_adv_bycountry$`United States of America`, mf_adv_bycountry$Greece)$rho.c

# Female vs. Male:
ccc_gender <- DescTools::CCC(mf_adv_bygender$Male, mf_adv_bygender$Female)$rho.c

# Older vs. Younger:
ccc_age <- DescTools::CCC(mf_adv_byage$Older, mf_adv_byage$Younger)$rho.c


ccc_data <- bind_rows(ccc_country %>% mutate(var = "country"),
                      ccc_gender %>% mutate(var = "gender"),
                      ccc_age %>% mutate(var = "age_group")) %>% 
  select(var, obs_ccc = est)

```

Get bootstrap CIs for the CCCs:
```{r}

# Function to bootstrap:
bootstrap_CCC <- function(data, i) {

  group1 <- pull(data[, 3])
  group2 <- pull(data[, 4])

  # Run and retrieve CCC:
  DescTools::CCC(group1[i], group2[i])$rho.c[1, 1]

}

# Overarching function to obtain percentile bootstrap CIs:
getbootcis <- function(data) {
  
  # Bootstrap CI:
  boot_ccc <- boot(data, bootstrap_CCC, 1000)
  boot_ci <- boot.ci(boot_ccc)$percent
  
  return(tibble(lower_ci = boot_ci[4],
                upper_ci = boot_ci[5]))
  
}

# Bootstrap CCC values and confidence intervals:
set.seed(1)

# Country:
bootci_country <- getbootcis(mf_adv_bycountry) %>% 
  mutate(var = "country")

# Gender:
bootci_gender <- getbootcis(mf_adv_bygender) %>% 
  mutate(var = "gender")

# Age:
bootci_age <- getbootcis(mf_adv_byage) %>% 
  mutate(var = "age_group")

# Incorporate values to ccc_data:
ccc_data <- ccc_data %>% 
  left_join(bind_rows(bootci_country, bootci_gender, bootci_age))

```

Figure 1:
```{r}

# Function to get scatter-plots:
plot_ccc <- function(data, Source) {
  
subsample1 <- pull(data[, 3])
subsample2 <- pull(data[, 4])
  
  ggplot(data = data,
         aes(x = subsample1, y = subsample2)) +
  geom_point(aes(color = Source)) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  scale_x_continuous(limits = c(-0.6, 0.6),
                      breaks = c(-.6, -.4, -.2, 0, .2, .4, .6)) +
  scale_y_continuous(limits = c(-0.6, 0.6),
                      breaks = c(-.6, -.4, -.2, 0, .2, .4, .6)) +
  scale_color_manual(values = c("green4", "red3")) +
  geom_abline() +
  theme_classic() + 
  labs(x = names(data)[3], y = names(data)[4])
  
}

# Plot United States vs. Greece:
aa_us_greece <- plot_ccc(mf_adv_bycountry, Source) +
  theme(legend.position = "none")

# Plot Males vs. Females:
aa_female_male <- plot_ccc(mf_adv_bygender, Source) +
  theme(legend.position = "none")

# Plot younger vs. Older:
aa_older_younger <- plot_ccc(mf_adv_byage %>% mutate(Source = ifelse(Source == "WVS/EVS", "WVS", Source)), Source) + 
  theme(legend.title = element_blank())


# Get graphs' labels:
ccc_labels <- ccc_data %>%
  mutate(label = sprintf("%.2f [%.2f, %.2f]", obs_ccc, lower_ci, upper_ci)) %>%
  select(var, label) %>%
  mutate(ccc = paste0("CCC = ", label))


# Figure 1:
cowplot::plot_grid(aa_us_greece +
                     geom_text(data = ccc_labels[ccc_labels$var == "country", ], aes(label = ccc), x = -.2, y = .5),
                   aa_female_male +
                     geom_text(data = ccc_labels[ccc_labels$var == "gender", ], aes(label = ccc), x = -.2, y = .5),
                   aa_older_younger +
                     geom_text(data = ccc_labels[ccc_labels$var == "age_group", ], aes(label = ccc), x = -.2, y = .5),
                   nrow = 1, align = "hv", labels = c("A", "B", "C"),
                   rel_widths = c(1, 1, 1.3))

ggsave("../figure1.jpeg", width = 12, height = 4)

```

Expected CCCs under true perfect agreement:
```{r}

# Calculate probability of belonging to a given group (e.g., prob. of being female):
get_prob <- function(data, group_var) {
  group_var <- enquo(group_var)
  
  data %>%
    drop_na(!!group_var) %>% 
    summarise(prob = mean(!!group_var == first(!!group_var))) %>% 
    mutate(var = as_label(group_var))
}

aa_long_id <- aa_long %>% 
  distinct(id, country, gender, age_group)

# Probability table:
prob_table <- bind_rows(
  get_prob(aa_long_id, country),
  get_prob(aa_long_id[aa_long_id$gender != "Other", ], gender),
  get_prob(aa_long_id, age_group))

ccc_data <- left_join(ccc_data, prob_table)

# For each group, simulate 1,000 random splits of the pool of participants, and measure the agreement (CCC) between the two sub-samples in each split:
estimate_random_group_ccc <- function(data, p = .5) {
  
  # Randomly split the data:
  rand_split <- data %>% 
    distinct(id) %>% 
    mutate(rand_gr = rbinom(n = n(), size = 1, prob = p),
           rand_gr = factor(rand_gr))

  data %>% 
    left_join(rand_split, by = "id") %>% 
    # Calculate pro-positions' hflv advantage:
    group_by(issue, position, mf, rand_gr) %>%
    summarise(link = mean(value_sc, na.rm = TRUE), .groups = "drop") %>%
    spread(position, link) %>% 
    mutate(arg_adv = yes - no) %>% 
    select(-no, -yes) %>% 
    spread(mf, arg_adv) %>% 
    mutate(hflv_pro = (harm + fair + libe + viol)/4) %>% 
    select(rand_gr, issue, hflv_pro) %>%
    # calculate CCC:
    spread(rand_gr, hflv_pro) %>% 
    summarise(ccc = DescTools::CCC(`0`, `1`)$rho.c$est) %>% 
    pull(ccc)
}

make_1000_draws <- function(prob) {
  map_dbl(1:1000, ~estimate_random_group_ccc(aa_long, prob))
}

# This takes around 5 minutes to run:
ccc_data_complete <- ccc_data %>%
  mutate(rand_ccc = map(prob, make_1000_draws)) %>%
  mutate(p = map2_dbl(obs_ccc, rand_ccc, ~mean(.y < .x)),
         mean_rand = map_dbl(rand_ccc, mean))

```

## Hypothesis 2: Accounting for the Global Change in Moral Norms Using Argument Advantage.

Figure 2A: WVS/EVS
```{r}

# Get correlation and R2:
cor.test(wvsevs_trends$logit_est, wvsevs_trends$hflv, method = "pearson")

r2 <- sprintf("Rsq = %.2f", cor(wvsevs_trends$logit_est, wvsevs_trends$hflv)^2)

# Scatter plot: Estimated global change rate plotted against argument advantage. 
(fig2_wvsevs <- wvsevs_trends %>% 
  ggplot(aes(hflv, logit_est, label = label)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_smooth(method = lm, color = "midnightblue") +
  geom_point() +
  geom_text_repel() +
  annotate("text", x = -0.26, y = 0.51, label = r2) +
  scale_x_continuous(limits = c(-0.35, 0.55), n.breaks = 11) +
  labs(x = "Argument advantage",
       y = "Global change rate") +
  theme_classic(base_size = 13) +
  ggtitle("Opinions measured in the WVS"))

# Slope of change rate on argument advantage:
wvsevs_trends %>%
  lm(data = ., logit_est ~ hflv) %>% 
  summary()

```

Figure 2B: ISSP
```{r}

# Get correlation and R2:
cor.test(issp_trends$logit_est, issp_trends$hflv, method = "pearson")

r2 <- sprintf("Rsq = %.2f", cor(issp_trends$logit_est, issp_trends$hflv)^2)

# Scatter plot: Estimated global change rate plotted against argument advantage. 
(fig2_issp <- issp_trends %>% 
  ggplot(aes(hflv, logit_est, label = label)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_smooth(method = lm, color = "midnightblue") +
  geom_point() +
  geom_text_repel() +
  annotate("text", x = -0.4, y = 0.25, label = r2) +
  scale_x_continuous(limits = c(-0.5, 0.5), n.breaks = 11) +
  labs(x = "Argument advantage",
       y = "Global change rate") +
  theme_classic(base_size = 13) +
  ggtitle("Opinions measured in the ISSP"))

# Slope of change rate on argument advantage:
issp_trends %>%
  lm(data = ., logit_est ~ hflv) %>% 
  summary()

```

Combine plots:
```{r}

cowplot::plot_grid(fig2_wvsevs, fig2_issp, labels = "AUTO")

ggsave("../figure2.jpeg", dpi = 350, height = 5, width = 10)

```

Figure 3: Correlations between argument advantages and opinion change rates in each individual country.

Calculate time trends, by issue and country:
```{r}

# ISSP:
issp_common_issues_bysample <- issp_common_issues %>%
  group_nest(issue, label, sample, hflv) 

issp_trends_bysample <- issp_common_issues_bysample %>%
  mutate(logit_est = map_dbl(data, estimate_logit))

# WVS/EVS:
wvsevs_common_issues_bysample <- wvsevs_common_issues %>%
  group_nest(issue, label, sample, hflv) 

wvsevs_trends_bysample <- wvsevs_common_issues_bysample %>%
  mutate(logit_est = map_dbl(data, estimate_logit))


# Save trends for supplementary tables:
write_rds(issp_trends_bysample, "../data-processed/ISSP_trends-by-issue-and-country.rds")
write_rds(wvsevs_trends_bysample, "../data-processed/WVS_trends-by-issue-and-country.rds")

```

```{r}

# Get each country's correlation between argument advantages and opinion change rates:
cor_wvs <- wvsevs_trends_bysample %>%
  group_by(sample) %>% 
  summarise(r = cor(logit_est, hflv)) 

cor_issp <- issp_trends_bysample %>%
  group_by(sample) %>% 
  summarise(r = cor(logit_est, hflv)) 

cor_comb <- bind_rows(
  cor_issp %>% mutate(source = "ISSP"), 
  cor_wvs %>% mutate(source = "WVS")
)

# Box-plots:
cor_comb %>% 
  mutate(source = fct_rev(source)) %>% 
  ggplot(aes(x = source,  y = r)) +
  geom_boxplot() +
  geom_point(position = position_jitter(width = .05)) +
  ggrepel::geom_text_repel(aes(label = sample), size = 3, max.overlaps = 14) +
  geom_hline(yintercept = 0, color = "grey50") +
  labs(x = NULL, y = "Correlation between argument advantage\nand opinion change rate") +
  annotate("text", x = 0.5, y = 1, label = "A", fontface = "bold", size = 6) +
  annotate("text", x = 1.5, y = 1, label = "B", fontface = "bold", size = 6) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

ggsave("../figure3.jpeg", dpi = 350, width = 10, height = 7)

```













