---
title: "R Notebook"
output: html_notebook
---

```{r}

library(tidyverse)

```

# Read data:
```{r}

# Time trends by issue and country:
issp_trends_bysample <- read_rds("../data-processed/ISSP_trends-by-issue-and-country.rds")
wvsevs_trends_bysample <- read_rds("../data-processed/WVS_trends-by-issue-and-country.rds")

# Argument advantage data:
aa_long <- read_rds("../data-processed/argument-advantage-data_US & Greece_long_clean.rds")

```

# Supplementary table 1: Opinion change rates estimated in WVS data. 
```{r}

wvsevs_trends_bysample %>% 
  select(sample, label, logit_est) %>% 
  mutate(logit_est = round(logit_est, 2)) %>% 
  spread(label, logit_est) %>% 
  rename(Country = sample) %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_classic()

```

# Supplementary table 2: Opinion change rates estimated in ISSP data. 
```{r}

issp_trends_bysample %>% 
  select(sample, label, logit_est) %>% 
  mutate(logit_est = round(logit_est, 2)) %>% 
  spread(label, logit_est) %>% 
  rename(Country = sample) %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_classic()

```

# Supplementary table 3: Wordings of opinion items.
```{r}

aa_long %>% 
  distinct(source, issue, wording) %>%
  rename(opinion = issue) %>% 
  rename_all(~str_to_title(.)) %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_classic()

```

# Supplementary table 4: Robustness check: mixed-level analysis of the effect of argument advantage on opinion change rates. 
See script '05_hypothesis2-robustness-check.Rmd'

# Supplementary tabl 5: Sample size per item, per country (summed across survey years) in the WVS data.
```{r}

wvsevs_trends_bysample %>% 
  unnest() %>% 
  group_by(sample, label) %>% 
  summarise(sum(n_sample)) %>% 
  spread(label, `sum(n_sample)`) %>% 
  rename(Country = sample) %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_classic()

```

# Supplementary table 6: Sample size per item, per country (summed across survey years) in the ISSP data.
```{r}

issp_trends_bysample %>% 
  unnest() %>% 
  group_by(sample, label) %>% 
  summarise(sum(n_sample)) %>% 
  spread(label, `sum(n_sample)`) %>% 
  rename(Country = sample) %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_classic()

```

# Supplementary table 7: Number of times an item was included in the WVS.
```{r}

wvsevs_trends_bysample %>% 
  unnest() %>% 
  group_by(sample, label) %>% 
  summarise(n_distinct(year)) %>% 
  spread(label, `n_distinct(year)`) %>% 
  rename(Country = sample) %>%
  kableExtra::kbl() %>% 
  kableExtra::kable_classic()

```

# Supplementary table 8: Number of times an item was included in the ISSP
```{r}

issp_trends_bysample %>% 
  unnest() %>% 
  group_by(sample, label) %>% 
  summarise(n_distinct(year)) %>% 
  spread(label, `n_distinct(year)`) %>% 
  rename(Country = sample) %>%
  kableExtra::kbl() %>% 
  kableExtra::kable_classic()

```
















